Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-12-20 ms.tex
Using "steady-state" as an adjective and "steady state" as a noun

In Fig. \ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Equation (\ref{eq:H0surf}). Additional spatial modes contribute to the solutions' accuracy in the core of the line. If more spatial modes are calculated, the agreement with the steady state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x=x_s=0$. If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over eigenmodes which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum. Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would primarily affect the distribution at late times due to the large mean diffusion time of photons near the line core. This was the motivation for choosing a comparatively low number of spatial eigenmodes with respect to the number of frequency eigenmodes calculated.

@@

\subsection{Steady State Source}
A primary goal of this work is to present a solution for resonant scattering of photons near the line-center frequency $\nu_0$ in a uniform sphere. We have generalized a spherically symmetric solution derived by \citet{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center. We introduce a new term to this solution, $J_{\rm bc}$, which allows the boundary condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere. This is solved using a continuous Fourier expansion in frequency. The integrals are discretized and the Fourier coefficients solved for numerically. The resulting flux correction, $H_{\rm bc}$, scales as $H_0(a\tau_0)^{-1/3}$. Thus, for large $a\tau_0$, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower $a\tau_0$. Since the Laplacian form of the differential equation is only correct when the line profile is $\phi \approx a/(\pi x^2 \Delta)$, our solutions do not accurately model the Doppler core of the \lya line. Because the peak of the spectral energy distribution of escaping photons is $x_{\rm peak} {\sim} (a\tau_0)^{1/3}$, calculations performed at small $a\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.

>>>>

In Fig. \ref{fig:steadystate}, the spectrum for $x_s=0$ and $\tau_0=10^7$ is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Equation (\ref{eq:H0surf}). Additional spatial modes contribute to the solutions' accuracy in the core of the line. If more spatial modes are calculated, the agreement with the steady-state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x=x_s=0$. If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over eigenmodes which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum. Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would primarily affect the distribution at late times due to the large mean diffusion time of photons near the line core. This was the motivation for choosing a comparatively low number of spatial eigenmodes with respect to the number of frequency eigenmodes calculated.

@@

\subsection{Steady-State Source}
A primary goal of this work is to present a solution for resonant scattering of photons near the line-center frequency $\nu_0$ in a uniform sphere. We have generalized a spherically symmetric solution derived by \citet{2006ApJ...649...14D} (called $H_0$ here) to allow a monochromatic source of photons with frequencies away from line center. We introduce a new term to this solution, $J_{\rm bc}$, which allows the boundary condition $J=\sqrt{3}H$ to be satisfied at the surface of the sphere. This is solved using a continuous Fourier expansion in frequency. The integrals are discretized and the Fourier coefficients solved for numerically. The resulting flux correction, $H_{\rm bc}$, scales as $H_0(a\tau_0)^{-1/3}$. Thus, for large $a\tau_0$, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower $a\tau_0$. Since the Laplacian form of the differential equation is only correct when the line profile is $\phi \approx a/(\pi x^2 \Delta)$, our solutions do not accurately model the Doppler core of the \lya line. Because the peak of the spectral energy distribution of escaping photons is $x_{\rm peak} {\sim} (a\tau_0)^{1/3}$, calculations performed at small $a\tau_0$ are inaccurate due to the close proximity of the spectral peak and the Doppler core of the line.
